---
title: "Cognitive effort-based decision-making across experimental and daily life indices in younger and older adults"
author: "Jennifer L. Crawford"
date: "`r Sys.Date()`"
output:
  html_document: default
  code_folding: "hide"
---
## Examine framing effects on effort-based decision-making in younger and older adults

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())

# Packages
library(correlation); library(lme4); library(lmerTest); library(sjstats); library(sjPlot); library(ggeffects); library(ggpubr); library(knitr); library(RColorBrewer); library(tidyverse);
source("summarySEwithin2.R")

#Create data directories
coged.path<-"https://raw.githubusercontent.com/jlcrawford/OA_CogED_online/master/Data/gain_loss_coged_SHARE.csv"
coged.full.path <-"https://raw.githubusercontent.com/jlcrawford/OA_CogED_online/master/Data/gain_loss_coged_full_SHARE.csv"
EMA.path <- "https://raw.githubusercontent.com/jlcrawford/OA_CogED_online/master/Data/CogEffort_ExpSamp_SHARE.csv"

#Make data frames for Cog-ED
coged<- read.csv(coged.path, header = T)
coged.full <-read.csv(coged.full.path, header = T)
```

```{r, Demo, warning = F, message = F}
#Pulling out participant IDs for completed Cog-ED runs
Subject.IDs <- coged %>% filter(completed == 1) %>% select(subjectid) %>% distinct(subjectid, .keep_all = TRUE)
```

```{r SV_CogED, warning=F, message=F}
#clean data frame with Cog-ED SV estimates and transform data across so that SV estimates are equivalent across both domains (i.e., gain, loss)
d.coged <- coged %>% distinct(subjectid, .keep_all = TRUE) %>% inner_join(Subject.IDs, by = "subjectid") %>% select(subjectid, ageGroup, taskOrder, IP12_1, IP12_2, IP12_3, IP13_1, IP13_2, IP13_3, IP14_1, IP14_2, IP14_3,IP12_1_loss, IP12_2_loss, IP12_3_loss, IP13_1_loss, IP13_2_loss, IP13_3_loss, IP14_1_loss, IP14_2_loss, IP14_3_loss, hitrate_N1, hitrate_N2, hitrate_N3, hitrate_N4, CRrate_N1, CRrate_N2, CRrate_N3, CRrate_N4) %>%
  group_by(subjectid, ageGroup) %>%
  mutate(SV_red__gain = (IP12_1/2 + IP12_2/3 + IP12_3/4)/3,
         SV_blue__gain = (IP13_1/2 + IP13_2/3 + IP13_3/4)/3,
         SV_purple__gain = (IP14_1/2 + IP14_2/3 + IP14_3/4)/3,
         SV_red__loss = ((IP12_1_loss/2 + IP12_2_loss/3 + IP12_3_loss/4)/3)*-1,
         SV_blue__loss = ((IP13_1_loss/2 + IP13_2_loss/3 + IP13_3_loss/4)/3)*-1,
         SV_purple__loss = ((IP14_1_loss/2 + IP14_2_loss/3 + IP14_3_loss/4)/3)*-1, 
         mean_HitRate = (hitrate_N1 + hitrate_N2 + hitrate_N3 + hitrate_N4)/4,
         meanCRrate = (CRrate_N1 + CRrate_N2 + CRrate_N3 + CRrate_N4)/4, 
         ACC = (mean_HitRate + meanCRrate)/2)

d.coged.SV <- d.coged %>% select(subjectid, ageGroup, taskOrder, SV_red__gain, SV_blue__gain, SV_purple__gain, SV_red__loss, SV_blue__loss, SV_purple__loss, mean_HitRate) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -c(subjectid, ageGroup, taskOrder, mean_HitRate)) %>%
  separate(col = tmp, into=c("Task","Condition"), sep = "__") %>%
  separate(col = Task, into=c(NA,"Task"), sep = "_") %>%
  mutate(Condition = factor(Condition, levels = c("gain","loss"), labels = c("Gain","Loss")),
         taskCode = factor(Task, levels=c("red","blue","purple"), labels=c(-1,0,1)),
         conditionCode = factor(Condition, levels = c("Gain","Loss"), labels = c(0,1)),
         ageCode = factor(ageGroup, levels = c("Young", "Old"), labels = c(0,1)),
         orderCode = factor(taskOrder, levels = c(1,2), labels = c(0,1)))
d.coged.SV$taskCode <- as.numeric(as.character(d.coged.SV$taskCode))
d.coged.SV$conditionCode <- as.numeric(as.character(d.coged.SV$conditionCode))
d.coged.SV$ageCode <- as.numeric(as.character(d.coged.SV$ageCode))
d.coged.SV$orderCode <- as.numeric(as.character(d.coged.SV$orderCode))
```

## Cognitive Effort Discounting

```{r CogED_Plot, warning = F, message = F}
CogED_sum <- summarySEwithin2(d.coged.SV, measurevar = "SV", withinvars = c("Task","Condition"), betweenvars = "ageGroup", idvar = "subjectid")
CogED_sum$Task <- factor(CogED_sum$Task, levels = c("red","blue","purple"), labels = c("2-Back","3-Back","4-Back"))

CogED_order_sum <- summarySEwithin2(d.coged.SV, measurevar = "SV", withinvars = c("Task","Condition"), betweenvars = c("taskOrder", "ageGroup"), idvar = "subjectid")
CogED_order_sum$Task <- factor(CogED_order_sum$Task, levels = c("red","blue","purple"), labels = c("2-Back","3-Back","4-Back"))

d.coged.SV$Task <- factor(d.coged.SV$Task, levels = c("red","blue","purple"), labels = c("2-Back","3-Back","4-Back"))
```

## Figure 1: Cognitive effort discounting across gain and loss incentive contexts in younger and older adults

```{r Fig1, warning=FALSE, message=FALSE}
#Plotting SV across both gain and loss domains
inaug_2021 <- c("#5445b1", "#749dae", "#f3c483", "#5c1a33", "#cd3341","#f7dc6a")

fig.1 <- ggplot(CogED_sum, aes(x=Task, y=SV, fill=Task)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_point(data = d.coged.SV, aes(x=Task, y=SV, color=Task),
             stat="identity", alpha=0.7, position = "jitter") +
  geom_bar(stat="identity", position=position_dodge(), alpha = .6) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2, size=1.1) + 
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(breaks=NULL) +
  xlab("") + ylab("Subjective Value") + facet_grid(.~Condition + ageGroup) +
  scale_color_manual(values = inaug_2021) + scale_fill_manual(values = inaug_2021)
fig.1
```

## Summarizing effects of task level, condition, and age group on discounting (SV estimates)

```{r MLM_CogED_SV, warning=FALSE, message=FALSE}
#multilevel model of SV (DV) with task level, condition (gain, loss), and age (young, old)
m.coged <- lmer(data = d.coged.SV, SV ~ taskCode*conditionCode*ageCode + (1 | subjectid))
summary(m.coged)

#breaking down the task x condition interaction
test.2back <- t.test(data = d.coged.SV %>% filter(taskCode == -1), SV ~ conditionCode, paired = T)
test.2back
test.3back <- t.test(data = d.coged.SV %>% filter(taskCode == 0), SV ~ conditionCode, paired = T)
test.3back
test.4back <- t.test(data = d.coged.SV %>% filter(taskCode == 1), SV ~ conditionCode, paired = T)
test.4back

#Creating data frame with average subjective value estimates in gain and loss domains
Cog_ED_ind_SV <- d.coged %>%
  mutate(meanSV_gain = (SV_red__gain + SV_blue__gain + SV_purple__gain)/3,
         meanSV_loss = (SV_red__loss + SV_blue__loss + SV_purple__loss)/3, 
         mean_HitRate = (hitrate_N1 + hitrate_N2 + hitrate_N3 + hitrate_N4)/4,
         LossGain_diff = meanSV_loss-meanSV_gain,
         GainLoss_diff = meanSV_gain-meanSV_loss)

#Calculating correlation across gain & loss incentive contexts
corr.YA.GainLoss <- cor_test(data = Cog_ED_ind_SV %>% filter(ageGroup == "Young"), "meanSV_gain", "meanSV_loss")
corr.YA.GainLoss

corr.OA.GainLoss <- cor_test(data = Cog_ED_ind_SV %>% filter(ageGroup == "Old"), "meanSV_gain", "meanSV_loss")
corr.OA.GainLoss
```

### Adding task order to the models predicting SV
#### 1= Gain first, Loss Second; 2= Loss first, Gain second

```{r orderEffects, warning = F, message = F}
#testing for order effects in SV estimates
m.coged.order <- lmer(data = d.coged.SV, SV ~ taskCode*conditionCode*ageCode + orderCode + (1 | subjectid))
summary(m.coged.order)
```

## Table 1: The effects of task level, condition, age group, and task order on subjective value

```{r Table1, warning=FALSE, message=FALSE}
table.1 <- tab_model(m.coged, m.coged.order, show.stat = TRUE, file = "table1.doc")
table.1
```

### Exploratory Analysis: Extracting residuals from linear model of loss SV estimates predicting gain SV estimates

```{r, RewardMotiv, warning=FALSE, message=FALSE}
m.coged.resid <- lm(data = Cog_ED_ind_SV, meanSV_gain ~ meanSV_loss)
summary(m.coged.resid)
coged.resids <- (summary(m.coged.resid))$residuals
Cog_ED_ind_SV$coged.resids <- coged.resids
```

# EMA Data

```{r importdata, echo = TRUE}
#Import concatenated EMA data
codebook.path <- "https://raw.githubusercontent.com/jlcrawford/OA_CogED_online/master/Data/Codebook.csv"
codebook <- read.csv(codebook.path, header = T)
#create list of new variable names from codebook
new.names <- codebook$new_itemname

#read in EMA data
EMA<- read.csv(EMA.path, header = T) %>% inner_join(Subject.IDs, by = "subjectid")

#clean up extraneous variables from Qualtrics survey
EMA.clean <- EMA %>% select(-c(EndDate, RecordedDate, Status, IPAddress, Progress, Finished, ResponseId, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference,LocationLatitude,LocationLongitude, DistributionChannel, UserLanguage, SC0)) %>%
  setNames(new.names) %>%
  separate(date, c("date", "time"), sep = " ") %>%
  mutate(Date = as.Date.character(date, "%m/%d/%y"),
         day = weekdays(Date),
         timeDay = if_else(time < 12, "morning", if_else(time > 18, "evening", "afternoon")))
```

## Summarizing the average number of activities endorsed per ping

```{r Activities, warning=FALSE, message=FALSE}
EMA.activities <- EMA.clean %>% select(subjectid, day, timeDay, activities) %>% filter(activities > 0) %>%
  mutate(activities.count = count.fields(textConnection(activities), sep = ","))
EMA.activities.sum <- EMA.activities %>% summarise(mean.activities = mean(activities.count), sd.activities = sd(activities.count), range.activities = range(activities.count))
```

## Mental Demand of Current Activities

```{r cogeffort, echo = TRUE}
#create data frame of mental demand ratings
m.demand <- EMA.clean %>% select(subjectid,ageGroup,time,timeDay,day,starts_with("demand_")) %>%
  pivot_longer(names_to = "category", values_to = "rating", -c(subjectid, ageGroup, time, timeDay, day)) %>%
  separate(col = category, into=c(NA,"Category"), sep = "_") 

#summarizing average mental demand of activities across all participants
m.demand.subj.av <-m.demand %>% group_by(subjectid, ageGroup) %>%
  summarise(count.demand = sum(!is.na(rating)),
         mean.demand = mean(rating, na.rm=T),
         iSD.demand = sd(rating, na.rm=T)) %>%
  filter(count.demand > 3)

m.demand.subj.IDs <- m.demand.subj.av %>% select(subjectid)

#testing for effects of SV and level-1 predictors (e.g., time of day, day of week) on mental demand ratings
m.demand.clean <- m.demand %>%
  mutate(ageCode = factor(m.demand$ageGroup, levels = c("Young", "Old"), labels = c(0,1)),
         dayCode = factor(day, levels = c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"),
                          labels = c(0,1,2,3,4,5,6)),
         timeCode = factor(timeDay, levels = c("morning","afternoon","evening"), 
                           labels = c(-1,0,1))) %>%
  filter(!is.na(rating)) %>% inner_join(Cog_ED_ind_SV) %>% inner_join(m.demand.subj.IDs) %>%
  mutate(meanSV_gain_c = scale(meanSV_gain, center = T, scale = F),
         meanSV_loss_c = scale(meanSV_loss, center = T, scale = F))
m.demand.clean$rating <- as.numeric(as.character(m.demand.clean$rating))
m.demand.clean$ageCode <- as.numeric(as.character(m.demand.clean$ageCode))
m.demand.clean$dayCode <- as.numeric(as.character(m.demand.clean$dayCode))
m.demand.clean$timeCode <- as.numeric(as.character(m.demand.clean$timeCode))

#null model of mental demand
m.mental.demand <- lmer(data = m.demand.clean, rating ~ 1 + (1 | subjectid))
summary(m.mental.demand)
icc(m.mental.demand)

# age + day of the week + time of the day + average Gain SV + average Loss SV (with age interactions) predicting mental demand
m.mental.demand.age.timeDay.Gainloss.int<- lmer(data = m.demand.clean, rating ~ ageCode + dayCode + timeCode + meanSV_gain_c*ageCode + meanSV_loss_c*ageCode + (1 | subjectid))
summary(m.mental.demand.age.timeDay.Gainloss.int)

# age + day of the week + time of the day + average Gain SV + average Loss SV (with age interactions) predicting mental demand (YAs ONLY)
m.mental.demand.age.timeDay.Gainloss.int.YA<- lmer(data = m.demand.clean %>% filter(ageCode ==0), rating ~ dayCode + timeCode + meanSV_gain_c + meanSV_loss_c + (1 | subjectid))
summary(m.mental.demand.age.timeDay.Gainloss.int.YA)

# age + day of the week + time of the day + average Gain SV + average Loss SV (with age interactions) predicting mental demand (OAs ONLY)
m.mental.demand.age.timeDay.Gainloss.int.OA<- lmer(data = m.demand.clean %>% filter(ageCode ==1), rating ~ dayCode + timeCode + meanSV_gain_c + meanSV_loss_c + (1 | subjectid))
summary(m.mental.demand.age.timeDay.Gainloss.int.OA)
```

## Table 2: Effects of age, day of week, time of day, and subjective value on daily life mental demand

```{r table2, warning=FALSE, message=FALSE}
table.2 <- tab_model(m.mental.demand.age.timeDay.Gainloss.int, m.mental.demand.age.timeDay.Gainloss.int.YA, m.mental.demand.age.timeDay.Gainloss.int.OA, show.stat = TRUE, file = "table2.doc")
table.2
```

## Figure 2: Relationships between the costs of cognitive effort and daily life mental demand across gain and loss incentive contexts

```{r CogEDEMA, echo=TRUE, message=FALSE, warning=FALSE}
#extracting predicted values from multilevel model (gain)
CogED.gain.EMA <- ggpredict(m.mental.demand.age.timeDay.Gainloss.int, terms = c("meanSV_gain_c", "ageCode"))
p.gain.EMA <- ggplot(CogED.gain.EMA, aes(x, predicted, colour=group)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), linetype = 0, alpha=.1) +
  geom_line(size =1) + theme_classic() +
  scale_colour_brewer(palette = "Paired", "Age Group", labels = c("Younger","Older")) + labs(x="Subjective Value (Gain)",
                                                                                                              y="Predicted Mental Demand") 
#extracting predicted values from multilevel model (loss)
CogED.loss.EMA <- ggpredict(m.mental.demand.age.timeDay.Gainloss.int, terms = c("meanSV_loss_c", "ageCode"))
p.loss.EMA <- ggplot(CogED.loss.EMA, aes(x, predicted, colour=group)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), linetype = 0, alpha=.1) +
  geom_line(size =1) + theme_classic() +
  scale_colour_brewer(palette = "Paired", "Age Group", labels = c("Younger","Older")) + labs(x="Subjective Value (Loss)",
                                                                                                              y="Predicted Mental Demand") 
fig.2 <- ggarrange(p.gain.EMA, p.loss.EMA, labels = c("A", "B"), common.legend = TRUE)
fig.2
```

## Exploratory Analyses: reward motivation effects on daily life mental demand

```{r rewardMotive_EMA, warning=FALSE, message=FALSE}
# age + day of the week + time of the day + reward motivation residuals predicting mental demand
m.mental.demand.age.timeDay.resid <- lmer(data = m.demand.clean, rating ~ ageCode + dayCode + timeCode + coged.resids + (1 | subjectid))
summary(m.mental.demand.age.timeDay.resid)

# age + day of the week + time of the day + reward motivation residuals (+ age interaction) predicting mental demand
m.mental.demand.age.timeDay.resid.int <- lmer(data = m.demand.clean, rating ~ ageCode + dayCode + timeCode +  coged.resids*ageCode + (1 | subjectid))
summary(m.mental.demand.age.timeDay.resid.int)

# age + day of the week + time of the day + reward motivation residuals predicting mental demand (YAs ONLY)
m.mental.demand.age.timeDay.resid.YA <- lmer(data = m.demand.clean %>% filter(ageCode == 0), rating ~ dayCode + timeCode + coged.resids + (1 | subjectid))
summary(m.mental.demand.age.timeDay.resid.YA)

# age + day of the week + time of the day + reward motivation residuals predicting mental demand (OAs ONLY)
m.mental.demand.age.timeDay.resid.OA <- lmer(data = m.demand.clean %>% filter(ageCode == 1), rating ~ dayCode + timeCode + coged.resids + (1 | subjectid))
summary(m.mental.demand.age.timeDay.resid.OA)
```

## Table 3: Effects of age, day of week, time of day, and reward motivation on daily life mental demand

```{r table3, warning=FALSE, message=FALSE}
table.3 <- tab_model(m.mental.demand.age.timeDay.resid.int, m.mental.demand.age.timeDay.resid.YA, m.mental.demand.age.timeDay.resid.OA, show.stat = TRUE, file = "table3.doc")
table.3
```