---
title: "OA CogED Online"
author: "JC"
date: "4/02/2021"
output:
  html_document: default
  code_folding: "hide"
---
#Online Cog-ED Pilots (second iteration)

``` {r setup, warning=FALSE, message=FALSE}
rm(list=ls())

# Packages
library(lme4); library(knitr); library(kableExtra); library(RColorBrewer); library(tidyverse);
source("summarySEwithin2.R")

#Create data directories
coged.path<-"~/Box Sync/CCPLab_Aging_Studies/OA_Effort_EMA/Data/Online/CogED/coged_ema_gainloss.csv"
PTQ.path <- "~/Box Sync/CCPLab_Aging_Studies/OA_Effort_EMA/Data/Online/CogED/coged_ema_ptq.csv"
EMA.path <- "~/Box Sync/CCPLab_Aging_Studies/OA_Effort_EMA/Data/Online/EMA/Online_CogED_EMA.csv"

#Make data frames for Cog-ED and demographics info
coged<- read.csv(coged.path, header = T)
PTQ <- read.csv(PTQ.path, header = T)
```

``` {r SV_CogED, warning=F, message=F}
#clean data frame with Cog-ED SV estimates and transform data across so that SV estimates are equivalent across both domains (i.e., gain, loss)
d.coged <- coged %>% select(subjectid, groupid, agegroup, taskOrder, IP12_1, IP12_2, IP12_3, IP13_1, IP13_2, IP13_3, IP14_1, IP14_2, IP14_3,IP12_1_loss, IP12_2_loss, IP12_3_loss, IP13_1_loss, IP13_2_loss, IP13_3_loss, IP14_1_loss, IP14_2_loss, IP14_3_loss, hitrate_N1, hitrate_N2, hitrate_N3, hitrate_N4) %>%
  group_by(subjectid, agegroup) %>%
  mutate(SV_red__gain = (IP12_1/2 + IP12_2/3 + IP12_3/4)/3,
         SV_blue__gain = (IP13_1/2 + IP13_2/3 + IP13_3/4)/3,
         SV_purple__gain = (IP14_1/2 + IP14_2/3 + IP14_3/4)/3,
         SV_red__loss = ((IP12_1_loss/2 + IP12_2_loss/3 + IP12_3_loss/4)/3)*-1,
         SV_blue__loss = ((IP13_1_loss/2 + IP13_2_loss/3 + IP13_3_loss/4)/3)*-1,
         SV_purple__loss = ((IP14_1_loss/2 + IP14_2_loss/3 + IP14_3_loss/4)/3)*-1)

d.coged.SV <- d.coged %>% select(subjectid, agegroup, taskOrder, SV_red__gain, SV_blue__gain, SV_purple__gain, SV_red__loss, SV_blue__loss, SV_purple__loss) %>%
  pivot_longer(names_to = "tmp", values_to = "SV", -c(subjectid, agegroup, taskOrder)) %>%
  separate(col = tmp, into=c("Task","Condition"), sep = "__") %>%
  separate(col = Task, into=c(NA,"Task"), sep = "_") %>%
  mutate(taskCode = factor(Task, levels=c("red","blue","purple"), labels=c(-1,0,1)),
         conditionCode = factor(Condition, levels = c("gain","loss"), labels = c(0,1)),
         ageCode = factor(agegroup, levels = c("young", "old"), labels = c(0,1)))
d.coged.SV$conditionCode <- as.numeric(d.coged.SV$conditionCode)
d.coged.SV$ageCode <- as.numeric(d.coged.SV$ageCode)
```

##Cognitive Effort Discounting
####Plotted with YAs collected previously for visualization

``` {r CogED_Plot, warning = F, message = F}
CogED_sum <- summarySEwithin2(d.coged.SV, measurevar = "SV", withinvars = c("Task","Condition"), betweenvars = "agegroup", idvar = "subjectid")
CogED_sum$Task <- factor(CogED_sum$Task, levels = c("red","blue","purple"), labels = c("2-Back","3-Back","4-Back"))

CogED_order_sum <- summarySEwithin2(d.coged.SV, measurevar = "SV", withinvars = c("Task","Condition"), betweenvars = c("taskOrder", "agegroup"), idvar = "subjectid")
CogED_order_sum$Task <- factor(CogED_order_sum$Task, levels = c("red","blue","purple"), labels = c("2-Back","3-Back","4-Back"))

d.coged.SV$Task <- factor(d.coged.SV$Task, levels = c("red","blue","purple"), labels = c("2-Back","3-Back","4-Back"))
#Plotting SV across both gain and loss domains
p.1 <- ggplot(CogED_sum, aes(x=Task, y=SV, fill=Task)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge(), alpha = .6) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2) + 
  geom_point(data = d.coged.SV, aes(x=Task, y=SV, color=Task),
             stat="identity", alpha=0.7, position = "jitter") +
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(breaks=NULL) +
  xlab("") + ylab("Subjective Value") + ggtitle("Cognitive Effort Discounting") +
  facet_grid(.~Condition + agegroup)
p.1 + scale_fill_brewer(palette = "Set1") + scale_color_brewer(palette = "Set1")


p.2 <- ggplot(CogED_sum, aes(x=Task, y=SV)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2) + 
  geom_point(data = d.coged.SV, aes(x=Task, y=SV, group=subjectid),
             stat="identity", alpha=0.7) +
  geom_line(data = d.coged.SV, aes(x=Task, y=SV, group=subjectid, colour = factor(subjectid)), alpha = .5) +
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(breaks=NULL) +
  xlab("") + ylab("Subjective Value") + ggtitle("Cognitive Effort Discounting") +
  facet_wrap(.~Condition + agegroup)
p.CogED <- p.2 + guides(colour=FALSE) 
p.CogED
```

###Data Broken Down into Gain & Loss

``` {r CogED_OAs, warning = F, message = F}
Cog_ED_ind_SV <- d.coged %>%
  mutate(meanSV_gain = (SV_red__gain + SV_blue__gain + SV_purple__gain)/3,
         meanSV_loss = (SV_red__loss + SV_blue__loss + SV_purple__loss)/3, 
         mean_HitRate = (hitrate_N1 + hitrate_N2 + hitrate_N3 + hitrate_N4)/4,
         LossGain_diff = meanSV_loss-meanSV_gain)

#Plotting SV across both gain and loss domains
p.GL <-  ggplot(Cog_ED_ind_SV, aes(meanSV_gain, meanSV_loss)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_point() + geom_smooth(method=lm) +ggtitle("Gain vs. Loss Discounting") +
    xlab("Gain") + ylab("Loss")
p.GL + scale_colour_brewer(palette = "Paired")

#Plotting average hit rate on the N-Back versus SV (Gain Condition)
p.performance <-  ggplot(Cog_ED_ind_SV, aes(mean_HitRate, meanSV_gain)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_point() + geom_smooth(method=lm) +ggtitle("N-Back Performance & SV (Gain Condition)") +
    xlab("Average N-Back Hit Rate") + ylab("Gain")
p.performance + scale_colour_brewer(palette = "Paired")
```

##NASA TLX
####Plotted with YAs from previous sample for visualization

``` {r Self-Report, warning = F, message = F}
#Mental Demand Ratings
NASA.m.demand <- coged %>% select(subjectid, mentaldemand_1, mentaldemand_2, mentaldemand_3, mentaldemand_4) %>%
  group_by(subjectid) %>%
  pivot_longer(names_to = "mental_demand", values_to = "rating", -c(subjectid)) %>%
  separate(col = mental_demand, into=c(NA,"Task"), sep = "_") 
NASA_mdemand_sum <- summarySEwithin2(NASA.m.demand, measurevar = "rating", withinvars = c("Task"), betweenvars = c("agegroup"), idvar = "subjectid")
NASA_mdemand_sum$Task <- factor(NASA_mdemand_sum$Task, levels = c(1,2,3,4), labels = c("1-Back","2-Back","3-Back","4-Back"))

p.m.demand <- ggplot(NASA_mdemand_sum, aes(x=Task, y=rating, fill=agegroup)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("Task") + ylab("Mental Demand") + ggtitle("Self-Reported Mental Demand") 
p.m.demand + labs(fill = "Age Group") + scale_fill_brewer(palette = "Paired")

#Frustration Ratings
NASA.frust <- coged %>% select(subjectid, agegroup, frustration_1, frustration_2, frustration_3, frustration_4) %>%
  group_by(subjectid, agegroup) %>%
  pivot_longer(names_to = "frustration", values_to = "rating", -c(subjectid, agegroup)) %>%
  separate(col = frustration, into=c(NA,"Task"), sep = "_") 
NASA_frust_sum <- summarySEwithin2(NASA.frust, measurevar = "rating", withinvars = c("Task"), betweenvars = c("agegroup"), idvar = "subjectid")
NASA_frust_sum$Task <- factor(NASA_frust_sum$Task, levels = c(1,2,3,4), labels = c("1-Back","2-Back","3-Back","4-Back"))

p.frust <- ggplot(NASA_frust_sum, aes(x=Task, y=rating, fill=agegroup)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("Task") + ylab("Frustration") + ggtitle("Self-Reported Frustration") 
p.frust + labs(fill = "Age Group") + scale_fill_brewer(palette = "Paired")
```

##Post-Task Questionnaire
####Only OA pilot sample plotted (only sample we have these data from)

``` {r PTQ, warning = F, message = F}
PTQ.clean <- PTQ %>%  select(subject, ends_with("response")) %>% select(!contains("strat")) %>%
  pivot_longer(names_to = "condition", values_to = "rating", -subject) %>%
  separate(col = condition, into=c("dimension","condition"), sep = "_") %>%
  separate(col = condition, into=c("condition",NA), sep = "__")
 
PTQ_sum <- summarySEwithin2(PTQ.clean, measurevar = "rating", withinvars = c("dimension","condition"), idvar = "subject")
  
p.PTQ <- ggplot(PTQ_sum, aes(x=dimension, y=rating, fill=condition)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=rating-ci, ymax=rating+ci), width=.2) +  
  xlab("") + ylab("") + ggtitle("Post-Task Questionnaire") 
p.PTQ + labs(fill = "Condition") + scale_fill_brewer(palette = "Set1")

#OAs who showed flipped patterns of Cog-ED responding (i.e., steep discoutning in gain & shallow/almost no discounting in loss)
PTQ.clean.OAsubset <- PTQ.clean %>% filter(subject == "5ea29d4aeeb3d71b9b736017" | subject == "5ea3fc787c48522165e5e4a5" | subject == "5ea1950819664f04542a50bf")
PTQ_subset_sum <- summarySEwithin2(PTQ.clean.OAsubset, measurevar = "rating", withinvars = c("dimension","condition"), idvar = "subject")

p.PTQ.subset <- ggplot(PTQ_subset_sum, aes(x=dimension, y=rating, fill=condition)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  xlab("") + ylab("") + ggtitle("Post-Task Questionnaire (from subset of OAs who showed flipped responses, N=3)") 
p.PTQ.subset + labs(fill = "Condition") + scale_fill_brewer(palette = "Set1")

#self-reported strategies
PTQ.strat.subset <- PTQ %>% select(subject, contains("strat")) %>% select(!contains("latency")) %>%
  filter(subject == "5ea29d4aeeb3d71b9b736017" | subject == "5ea3fc787c48522165e5e4a5" | subject == "5ea1950819664f04542a50bf")
kable(PTQ.strat.subset)
```

####Avoidance = To what degree did you choose the easier task because you wanted to avoid difficulty?

####Caring = To what degree did you select tasks based on whether or not you would be able to win (or lose) money?

####Challenge = To what degree did you choose the harder task because you wanted to challenge yourself?

####Difficulty = To what degree were your choices based on the difficulty of each task?

####Effort = To what degree were your choices based on the amount of effort each task required?

####Maintenance = To what degree did you select tasks based on whether or not you would be able to maintain your effort?

####Money = To what degree were your choices based on the offer amount ($) of each task?

###Testing for differences in task order

``` {r orderEffects, warning = F, message = F}
#plotting results broken down by task order
##Order: 1=gain first, 2= loss first
p.Order <- ggplot(CogED_order_sum, aes(x=Task, y=SV, fill=Task)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge(), alpha = .6) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=SV-ci, ymax=SV+ci), width=.2) + 
  geom_point(data = d.coged.SV, aes(x=Task, y=SV, color=Task),
             stat="identity", alpha=0.7, position = "jitter") +
  coord_cartesian(ylim=c(0,1)) +
  scale_x_discrete(breaks=NULL) +
  xlab("") + ylab("Subjective Value") + ggtitle("Cognitive Effort Discounting (Order Effects)") +
  facet_grid(.~Condition + agegroup + taskOrder)
p.Order + scale_fill_brewer(palette = "Set1") + scale_color_brewer(palette = "Set1")
```

# EMA Data

``` {r importdata, echo = TRUE}
#Import concatenated EMA data
codebook.path <- "~/Box Sync/CCPLab_Aging_Studies/OA_Effort_EMA/Data/Online/EMA/Codebook.csv"
codebook <- read.csv(codebook.path, header = T)
#create list of new variable names from codebook
new.names <- codebook$new_itemname

#read in EMA data
EMA<- read.csv(EMA.path, header = T)

#clean up extraneous variables from Qualtrics survey
EMA.clean <- EMA %>% select(-c(EndDate, RecordedDate, Status, IPAddress, Progress, Finished, ResponseId, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, DistributionChannel, UserLanguage, SC0)) %>%
  setNames(new.names)
```

## Average Survey Duration (in seconds)

``` {r surveyDuration, echo = TRUE}
mean_duration <- mean(EMA.clean$duration, na.rm = T)
mean_duration
```

## Current Affect 

```{r affect, message=F, warning=F}
#creating data frame from affect ratings
current.affect <- EMA.clean %>% select(SubID, starts_with("affect_")) %>%
  pivot_longer(names_to = "Affect", values_to = "rating", -SubID) %>%
  separate(col = Affect, into=c(NA,"Affect_Term"), sep = "_") 

#summarizing average affect across all participants
affect.subj <-current.affect %>% group_by(SubID, Affect_Term) %>% 
  dplyr::summarise(mean.affect = mean(rating, na.rm = T))

affect.av <-current.affect %>% group_by(Affect_Term) %>%
  dplyr::summarise(mean.affect = mean(rating, na.rm = T))
affect.sum <- summarySEwithin2(affect.subj, measurevar = "mean.affect", withinvars = c("Affect_Term"), idvar = "SubID")

#plotting average affect ratings
affect.sum$Affect_Term <- factor(affect.sum$Affect_Term, levels = c("aroused", "excited", "happy", "calm", "fearful", "sluggish", "sad", "passive"), labels = c("Aroused", "Excited", "Happy", "Calm", "Fearful", "Sluggish", "Sad", "Passive"))
p.affect <- ggplot(affect.sum, aes(x = Affect_Term, y= mean.affect)) +
 theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean.affect-ci, ymax=mean.affect+ci), width=.2) +
  coord_cartesian(ylim=c(1,4)) +
  xlab("") + ylab("Affect Rating")
p.affect
```

## Current Activities 

``` {r currentactivities, echo = TRUE}
#Individual pie chart for item "What are you doing right now"
activities.string <- paste(EMA.clean$activities, collapse = "," )
activity.vector <- str_split(activities.string, ',')[[1]]
activity.clean <- data_frame(activity.vector)
activity_freq <- activity.clean %>% group_by(activity.vector) %>% tally() %>% filter(activity.vector !="") %>%
  rename(activity = activity.vector) %>%
  mutate(percentage = (n / sum(n))*100)
activity_freq$activity <- factor(activity_freq$activity, levels=c(1,2,14,12,16,4,7,20,21,6,19,10,8,5,15,9,3,13,18,11), labels=c("Eating or Drinking","TV", "Computer", "In Transit", "Reading", "Socializing", "Sleeping", "Chores","Listening to Speech", "Work", "Hygiene", "Cooking", "Errands", "Exercise", "Radio", "Cleaning", "Entertainment", "Nothing in Particular", "Volunteering", "Doctor's Appointment"))

kable(activity_freq, caption =  "Frequency of Current Activities")

p.activities <- ggplot(activity_freq, aes(x = activity, y= percentage)) +
 theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_bar(stat="identity", position=position_dodge()) +
  xlab("Activity") + ylab("Percentage of Time Spent in  Activity")
p.activities
```

## Mental Demand of Current Activities

``` {r cogeffort, echo = TRUE}
#create data frame of mental demand ratings
m.demand <- EMA.clean %>% select(SubID, starts_with("demand_")) %>%
  pivot_longer(names_to = "category", values_to = "rating", -SubID) %>%
  separate(col = category, into=c(NA,"Category"), sep = "_") 

#summarizing average mental demand of activities across all participants
m.demand.subj <-m.demand %>% group_by(SubID, Category) %>% filter(Category != "school") %>%
  dplyr::summarise(mean.demand = mean(rating, na.rm = T))

m.demand.subj.av <-m.demand %>% group_by(SubID) %>% filter(Category != "school") %>%
  dplyr::summarise(mean.demand = mean(rating, na.rm = T))

m.demand.av <-m.demand %>% group_by(Category) %>%
  dplyr::summarise(mean.demand = mean(rating, na.rm = T))
m.demand.sum <- summarySEwithin2(m.demand.subj, measurevar = "mean.demand", withinvars = c("Category"), idvar = "SubID")
m.demand.subj.sum <- summarySEwithin2(m.demand.subj, measurevar = "mean.demand", betweenvars = "SubID", idvar = "SubID")

#plotting mental demand associated with each of the surveyed activities
p.mental.demand <- ggplot(m.demand.sum, aes(x = Category, y= mean.demand)) +
 theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean.demand-se, ymax=mean.demand+se), width=.2) +
  coord_cartesian(ylim=c(1,3.5)) +
  xlab("Activity") + ylab("Mental Demand")
p.mental.demand

p.mental.demand.subj <- ggplot(m.demand.subj.av, aes(x = SubID, y= mean.demand)) +
 theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) +
    coord_cartesian(ylim=c(1,3)) +
  xlab("ID") + ylab("Mental Demand")
p.mental.demand.subj
#plotting mental demand as a frequency of reported daily life activities
m.demand.sum$Category <- factor(m.demand.sum$Category, levels = c("work", "volunteer", "doctor", "transit", "social", "exercise", "computer", "cleaning", "entertain", "cooking", "reading", "errand", "chores", "radio", "hygeine", "tv", "nothing", "eat", "sleep"), labels = c("Work", "Volunteering", "Doctor's Appt.", "In Transit", "Socializing", "Exercising", "Computer", "Cleaning", "Entertainment", "Cooking", "Reading", "Errands", "Chores", "Radio", "Hygiene", "TV", "Nothing in Particular", "Eating/Drinking", "Sleeping"))

p.mental.demand.freq <- ggplot(m.demand.sum, aes(x = Category, y= mean.demand)) +
 theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean.demand-ci, ymax=mean.demand+ci), width=.2) +
  coord_cartesian(ylim=c(1,3.3)) +
  xlab("Activity") + ylab("Mental Demand")
p.mental.demand.freq
#tabulating frequency of mental demand ratings (from 5-point likert scale)
m.demand$rating <- factor(m.demand$rating, levels=c(1,2,3,4,5), labels = c("Not at All","A Little Bit","Moderately", "Quite a Bit", "Extremely"))  
m.demand.freq <- m.demand %>% group_by(rating) %>% tally() %>% filter(rating != "NA")

kable(m.demand.freq, caption =  "Frequency of 'Mental Demand' Responses for Current Activities")

#plotting frequency of mental demand in daily life
m.demand.frequency <- ggplot(m.demand.freq, aes(x = rating, y= n)) +
 theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Not at All","A Little Bit","Moderately", "Quite a Bit", "Extremely")) +
  geom_bar(stat="identity", position=position_dodge()) + ggtitle("Mental Demand of Activities") + xlab("Mental Demand") + ylab("Frequency")
m.demand.frequency

CogED.ind.sum$mentalDemand <- m.demand.subj.av$mean.demand
cor.test(CogED.ind.sum$meanSV, CogED.ind.sum$mentalDemand)

OA_EMA_CogED <- ggplot(CogED.ind.sum, aes(meanSV, mentalDemand)) +
   theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
geom_point() + geom_smooth(method=lm) +ggtitle("") +
    xlab("Subjective Value") + ylab("Daily Life Mental Demand")
OA_EMA_CogED
```

## Social Engagement -- Social Partners

``` {r currentSocial, echo = TRUE}
EMA.clean$social_partner <- factor(EMA.clean$social_partner, levels=c(1,2,3,4,5,6), labels=c("Alone","Coworker","Friend", "Family Member", "Spouse/partner","Stranger"))
Social_freq <- EMA.clean %>% select(social_partner) %>% group_by(social_partner) %>% tally() %>% filter(social_partner != "NA")

kable(Social_freq, caption =  "Frequency of Social Engagement")

social_plot <- ggplot(Social_freq, aes(x = social_partner , y= n)) +
 theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_bar(stat="identity", position=position_dodge()) + ggtitle("Daily Life Social Engagement (Social Partner Type)") + xlab("") + ylab("Frequency")
social_plot
```